%
% resume.tex
% Seth Lakowske
%

\documentclass{article}
\usepackage{hyperref}

\pagestyle{empty}
\textwidth 7in
\textheight 10in
\oddsidemargin -.5in
\evensidemargin 0in
\topmargin 0in
\headsep 0in
\headheight 0in

\begin{document}
  \begin{center}

    \Large
    \textbf{Seth Lakowske} \\
    \normalsize

    \href{mailto:lakowske@gmail.com}{lakowske@gmail.com}
		      
    \medskip
    
    % \begin{tabular}{c}
    %   \textbf{Permanent Address} \\
    %   5144 Thorson Rd. \\
    %   Sun Prairie, WI 53590 \\
    % \end{tabular}

  \end{center}
  
  \begin{description}   
    
  \item \textsc{Objective}
    \begin{itemize}
    \item Obtain a position designing and developing software systems.
    \end{itemize}
    
    
  \item \textsc{Experience}
    
    \begin{itemize}

    \item
      \textbf{\href{http://www.thermofisher.com} {Thermo Fisher Scientific}, 2017 - 2021}

      Created a service mesh to secure service-to-service communication with Istio.  Deployed and managed a logging and
      monitoring framework consisting of Fluentd, Elastic Search, Kibbana and Prometheus. Researched multiple API gateways 
      to route requests to services.
      
    \item
      \textbf{\href{http://coreinformatics.com} {Core Informatics}, 2016 - 2017}

      Lead a technical team creating a microservice architecture to expand the company's ability to grow into a more reliable
      and extensive environment.  Investigated cluster software Apache Mesosphere and Kubernetes to host
      microservices.  Converted legacy applications to Docker images running inside Kubernetes.  Acquired
      by Thermo Fisher Scientific.
      
      
    \item
      \textbf{\href{http://www.mandli.com} {Mandli Communications}, 2008 - 2016}

      Created an automated road sign detection algorithm using OpenCV to replace manual road sign input.  
      Developed a road sign retro reflectivity product using Weka that is an innovation in the transportation industry. 
      Developed a method to model arbitrarily complex sensor placements on new road collection vehicles.
      Researched a pavement distress detection technique using grayscale images of the road.  
      Developed OpenGL based tools to inventory road assets.

    \item
      \textbf{\href{https://ppubs.uspto.gov/dirsearch-public/print/downloadPdf/20080249982} {Ohigo Inc.} , 2005 - 2008}
    
      Managed a team of developers that built a music search engine.
      Used Mel Frequency Cepstrum Coefficients (MFCC) and a decision tree
      to categorize music by genre.  Applied for a patent on this technique
      (Application \#20080249982). Used Solr search engine to query a 
      database of music knowledge.  Created a game, Music Streaker, 
      using small cash rewards to generate music knowledge.

     
    \end{itemize}

  \item \textsc{Education}
    \begin{itemize}
    \item \textbf{\href{http://www.wisc.edu/} {University of Wisconsin, Madison}}.  Completed a BS at the
      \href{http://www.cs.wisc.edu/}{Department of Computer Sciences} in May, 2005.
    \end{itemize}
    
  \item \textsc{Skills}
    \begin{itemize}
      \item Containerization with Docker and Kubernetes 
      \item Extensive experience with Java, Spring and IoC
      \item Vision Programming using JavaCV, OpenCV and ImageIO
      \item Machine Learning using Weka
      \item Database Programming, SQL, JPA and JPQL
      \item Experienced with C, C++, Python, PHP and Matlab
      \item Development with gcc, gdb, make and associated tools
      \item Comfortable on GNU/Linux, OS X and Windows operating systems
    \end{itemize}
    
  \item \textsc{Technical Interests}
    \begin{itemize}
    \item Machine Learning and Artificial Intelligence
    \item Computer Vision
    \item Generative AI
    \end{itemize}
    
  \item \textsc{References}
    \begin{itemize}
    \item Available upon request
    \end{itemize}
    
  \end{description}
\end{document}
